---
title: 'Lab Week 3: Binomial Logistic Regression'
author: "Grace Bianchi"
date: "2023-01-26"
output: html_document
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE, echo = TRUE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(GGally)
library(jtools)
library(AICcmodavg)
```

# Psuedocode

* Examine our data(plots, tables, summary stats)
* Identify a question
* Wrangle the data
* Identify same candidate models
* Select among candidate models using AIC/BIS
* Select among canditate models using K-fold cross validation
* Select among candidate models using area under Reciever Operating Characteristic Curve

```{r}
GGally::ggpairs(penguins %>% select(species, bill_length_mm:sex), 
                aes(color = species))

```


```{r}
class(penguins$species)
levels(penguins$species)

adelie_chinstrap <- penguins %>% 
  filter(species %in% c("Adelie", "Chinstrap")) %>% 
  mutate(species = fct_drop(species)) %>% 
  select(-year) %>% 
  drop_na()

levels(adelie_chinstrap$species)
```
# Let's check out the trends across variables

```{r}
ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y = flipper_length_mm)) +
  geom_point(aes(color = sex, shape = island)) +
  facet_wrap(~ species)

ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y = bill_length_mm)) + 
  geom_point(aes(color = sex, shape = island)) +
  facet_wrap(~ species)
```


# Let's do some binary logistic regression!

```{r}
f1 <- species ~ body_mass_g + flipper_length_mm + sex

ad_chin_blrl <- glm(formula = f1, data = adelie_chinstrap,
                    family = "binomial")

ad_chin_blrl
summary(ad_chin_blrl)

blrl_tidy <- tidy(ad_chin_blrl)
```


```{r}
ggplot(data = adelie_chinstrap, aes(x = species, y = body_mass_g)) +
  geom_jitter(aes(color = sex))

```

```{r}
blrl_fitted <- ad_chin_blrl %>% 
  broom::augment(type.predict = "response")

ggplot(data = blrl_fitted, aes(x = flipper_length_mm, y = .fitted)) +
  geom_point(aes(color = sex, shape = species)) +
  geom_smooth(aes(color = sex), se = FALSE) +
  labs(x = "Flipper Length (mm)", 
       y = "Probability of outcome(Chinstrap)")
```

# Predictions for new values with predict()

```{r}
ex1 <- predict(ad_chin_blrl, 
               data.frame(sex = "female",
                          body_mass_g = 3410,
                          flipper_length_mm = 192),
               type = 'response')


new_df <- data.frame(
  sex = c("male", "female", "female"),
  body_mass_g = c(3298, 4100, 3600),
  flipper_length_mm = c(212, 175, 180)
)

ex2 <- predict(ad_chin_blrl, new_df, type = 'response')

```

## Create a new binary logistic model
```{r}
f2 <- species ~ bill_length_mm + body_mass_g


ad_chin_blr2 <- glm(formula = f2,
                    data = adelie_chinstrap,
                    family = "binomial")
```

## Model Selection

```{r}
AICcmodavg::aictab(list(ad_chin_blrl, ad_chin_blr2))
AICcmodavg::bictab(list(ad_chin_blrl, ad_chin_blr2))
```
10-fold Cross Validation

```{r}
set.seed(123)

n_folds <- 10
fold_vec <- rep(1:n_folds, length.out = nrow(adelie_chinstrap))

ad_chin_kfold <- adelie_chinstrap %>% 
  mutate(fold = sample(fold_vec, size = n(), replace = FALSE))

```

purrr::map()

```{r}
x_vec <- 1:10
thing <- purrr::map(.x = x_vec, ### a sequence (vector, list)
                    .f = sqrt) ### a function
thing ## for loop is kinda slow, this function runs more efficiently

my_funct <- function(x, y, z) {
  return((x - y)^z)
}

thing2 <- purrr::map(.x = x_vec,
                     .f = my_funct,
                     y = 2, z = 3)
thing2

```
 
```{r}
pred_acc <- function(x, y) {
  accurate <- ifelse(x ==y, 1, 0)
  
  return(mean(accurate, na.rm = TRUE))
}

calc_fold <- function(i, fold_df, f) {
  kfold_test <- fold_df %>% 
    filter(fold == i)
  kfold_train <- fold_df %>% 
    filter(fold != i)
  
  kfold_blr <- glm(f, data = kfold_train, family = 'binomial')
  
  kfold_pred <- kfold_test %>% 
    mutate(blr = predict(kfold_blr, kfold_test, type = 'response'),
           pred = ifelse(blr > 0.50, "Chinstrap", "Adelie"))
  
  kfold_accuracy <- kfold_pred %>% 
    summarize(blr_acc = pred_acc(species, pred))
  
  return(kfold_accuracy)
}
```
 
```{r}
n_folds <- 10

results1_purrr_df <- purrr::map(.x = 1:n_folds, # sequence of fold numbers
                                .f = calc_fold, # function
                                fold_df = ad_chin_kfold, # additional argument to calc_fold()
                                f = f1) %>%              # additional argument to calc_fold()
  bind_rows() %>%
  mutate(mdl = 'f1')

results2_purrr_df <- purrr::map(.x = 1:n_folds,
                               .f = calc_fold,
                               fold_df = ad_chin_kfold,
                               f = f2)
  
results_purrr_df <- bind_rows(results1_purrr_df, results2_purrr_df) %>% 
  group_by(mdl) %>% 
  summarize(mean_acc = mean(blr_acc))
```


# Tidymodels version

```{r}
### define model type
blr_model <- logistic_reg() %>% 
  set_engine("glm")

### set a basic regression
blr_tidyfit_f1 <-  blr_model %>% 
  fit(f1, data = adelie_chinstrap)
blr_tidyfit_f2 <- blr_model %>% 
  fit(f2, data = adelie_chinstrap)

blr_tidyfit_f1 %>% 
  tidy()
blr_tidyfit_f2 %>% 
  glance()
```

## Tidy kfold Cross Validation

```{r}
set.seed(345)

tidy_folds <- vfold_cv(adelie_chinstrap, v =10)

### use workflow to bundle model and formula
blr_tidy_wf1 <- workflow() %>% 
  add_model(blr_model) %>% 
  add_formula(f1)

blr_tidy_cv_f1 <- blr_tidy_wf1 %>% 
  fit_resamples(tidy_folds)

collect_metrics(blr_tidy_cv_f1)

### use workflow to bundle model and formula
blr_tidy_wf2 <- workflow() %>% 
  add_model(blr_model) %>% 
  add_formula(f2)

blr_tidy_cv_f2 <- blr_tidy_wf2 %>% 
  fit_resamples(tidy_folds)

collect_metrics(blr_tidy_cv_f2)

```
## Area under the curve

```{r}
blr_f1_pred <- adelie_chinstrap %>% 
  mutate(predict(blr_tidyfit_f1, .)) %>% 
  mutate(predict(blr_tidyfit_f2, . , type = 'prob'))

blr_f1_pred %>%
  roc_curve(truth = species, .pred_Adelie) %>%
  autoplot()

```

